---
title: "BIOL4408 Marine Ecology: lobster pots 1."
author: "TimLanglois"
date: "09/01/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# 1. Import lobster pot data

1. Import data - Tim has done tricky stuff in another script
2. Plot and describe the data.



Need to install a missing library
```{r}
# install.packages("ggmap")

```



Next we load some librarys
```{r libs1, message=FALSE, warning=FALSE}
library(tidyr) #to tidy data
library(dplyr) #to transform data
library(readr) #to write data
library(ggplot2) #to plot data
library(ggmap)
library(readr) #to write data
library(here) #to make robust links to files
```

It is useful to set a study name
```{r name, message=FALSE, warning=FALSE}
study<-"lobster.pots"
```



We are going to use the here() function, which creates a shortcut to your location.

```{r , message=FALSE, warning=FALSE}
here::here()
```





As long as the names on the folders are consistent this function will enable us to work across computers and operating systems.


If you are using an ecocloud server - we will have to add folder names to the here() function - but this should work

#here("workspace","Template-lobster-pots","Data")

Let's make a shortcut to that "Data" directory.
```{r , message=FALSE, warning=FALSE}

data.dir <- here::here("Data")

#or for ecocloud

#data.dir <- here("workspace","Template-lobster-pots","Data")
```


Let's make a plots directory and then shortcut to that directory.
```{r , message=FALSE, warning=FALSE}

dir.create(file.path(here::here(), "Plots")) #create Data folder

plot.dir <- here::here("Plots")

#or for ecocloud
#dir.create(file.path(here(), "workspace","Template-lobster-pots","Plots")) #create Data folder

#data.dir <- here("workspace","Template-lobster-pots","Plots")
```




Read in polygons of NTR------
```{r}

setwd(data.dir)
dir()
ntr<-read_csv("ntr.2019-01-23.csv")%>%
  glimpse()

```




Read in pot data
```{r}
setwd(data.dir)
dat<-read_csv("lobster.pots.2019-01-23.csv")%>%
  glimpse()

```





## Basic plots to check the data


# Get map of Rottnest

```{r}
# Bounding box
bbox <- c(115.435,-32.04,  115.57,-31.975)

# make the map
rotto.map<-(get_stamenmap(as.vector(bbox), zoom = 14, maptype="terrain"))

ggmap(rotto.map)


```




Plot all of pots

```{r}

ggmap(rotto.map)+
  geom_point(aes(lon,lat),size=2,colour="Yellow",data=dat, alpha=0.25)+
  xlab('Longitude')+
  ylab('Lattitude')

```



Plot of all pots with NTZs

```{r}
ggmap(rotto.map)+
  geom_point(aes(lon,lat,colour="red"),size=1,data=dat, alpha=0.25,show.legend = F)+
  geom_polygon(data = fortify(ntr%>%filter(lon<115.48)), aes(lon, lat, group = group), colour = "green", fill="orange",alpha = 0.5) +
  geom_polygon(data = fortify(ntr%>%filter(lon>115.48)), aes(lon, lat, group = group), colour = "green", fill="green",alpha = 0.25) +
xlab('Longitude')+
  ylab('Lattitude')

```


Plot of all pots faceted by year with NTRs

```{r}
ggmap(rotto.map)+
  geom_point(aes(lon,lat,colour="red"),size=1,data=dat, alpha=0.25,show.legend = F)+
  # geom_polygon(data = fortify(ntr), aes(lon, lat, group = group), colour = "green", fill="orange",alpha = 0.5) +
  
  geom_polygon(data = fortify(ntr%>%filter(lon<115.48)), aes(lon, lat, group = group), colour = "green", fill="orange",alpha = 0.5) +
  geom_polygon(data = fortify(ntr%>%filter(lon>115.48)), aes(lon, lat, group = group), colour = "green", fill="green",alpha = 0.25) +

  theme(axis.text=element_blank(),
        
        axis.title=element_blank(),
        axis.ticks=element_blank())+
  facet_wrap(~year,ncol=2)

```





## The pot data I have provided contains several 
Explore the pot distribution within different zones of the island with different metrics
To look for general patterns

# Plot with distance to NTR boundary

```{r}
unique(dat$zone)

ggplot(data=dat%>%filter(!zone=="W"), aes(x=dst_sank))+
  geom_density(alpha=.5)+
  facet_grid( .~ zone)+
  theme_classic()+
  xlab('Distance to sanctuary (m)')+
  ylab('Density')
```


Plot with depth - check out my labeller!
```{r}

labels <- c(N = "North", S = "South", W = "West")

ggplot(data=dat, aes(x=depth))+
  geom_density(alpha=.5)+
  facet_grid( .~ zone,labeller=labeller(zone = labels))

```


Plot with distance to jetties
```{r}
ggplot(data=dat, aes(x=dst_jettie))+
  geom_density(alpha=.5)+
  facet_grid( .~ zone,labeller=labeller(zone = labels))
```


Plot with distance to moorings
```{r}
ggplot(data=dat, aes(x=dst_moorin))+
  geom_density(alpha=.5)+
  facet_grid( .~ zone,labeller=labeller(zone = labels))

```




Plot with distance to coast
```{r}
pot.cst.hist<-ggplot(data=dat, aes(x=dst_cst))+
  geom_density(alpha=.5)+
  facet_grid( .~ zone,labeller=labeller(zone = labels))
pot.cst.hist
```










Go back to [Analysis-lobster-pots](https://github.com/UWA-BIOL4408-Marine-Ecology/Analysis-lobster-pots/blob/master/README.md)

Go forward to [2_lobster-pot-model](https://github.com/UWA-BIOL4408-Marine-Ecology/Analysis-lobster-density/blob/master/2_lobster-density_check-data.md)