---
title: "BIOL4408 Marine Ecology: lobster pots 1."
author: "TimLanglois"
date: "09/01/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# 2. Create Null lobster pot data


Need to install a missing library
```{r}
# install.packages("sm")

```



Load some librarys
```{r libs1, message=FALSE, warning=FALSE}
library(tidyr)
library(plyr)
library(dplyr)
library(ggplot2)
library(readr) #to write data
library(here) #to make robust links to files
# And you will need these libraries
library(ggmap)
library(sm)
library(KernSmooth)

```





It is useful to set a study name
```{r name, message=FALSE, warning=FALSE}
study<-"lobster.pots"
```



We are going to use the here() function, which creates a shortcut to your location.


Check what the here() function returns in your environment? and adapt to suit

Again - we have to use here::here() - due to conflict with plyr::here()
```{r , message=FALSE, warning=FALSE}
here::here()
```

If you are using an ecocloud server - you will probrably have to add folder names to the here() function 

#here::here("workspace","Template-lobster-pots","Data")

Let's make a shortcut to that "Data" directory.
```{r , message=FALSE, warning=FALSE}

data.dir <- here::here("Data")

#or for ecocloud

#data.dir <- here::here("workspace","Template-lobster-pots","Data")
```


Let's make a plots directory and then shortcut to that directory.
```{r , message=FALSE, warning=FALSE}

dir.create(file.path(here::here(), "Plots")) #create Data folder

plot.dir <- here::here("Plots")

#or for ecocloud
#dir.create(file.path(here(), "workspace","Template-lobster-pots","Plots")) #create Data folder

#data.dir <- here("workspace","Template-lobster-pots","Plots")
```



Read in pot data
```{r warning=FALSE}
setwd(data.dir)
dat<-read_csv("lobster.pots.2019-01-23.csv")%>%
  glimpse()

```
`





# Create Null using other data model for tests
```{r}

dat.pots<-dat%>%
  dplyr::select(dst_sank,zone,lat,lon,year)%>%
  mutate(Model="Pots")%>%
  glimpse()

summary1<-plyr::ddply(dat,.(zone), summarise,
                Max = max(dst_sank),
                Min = min(dst_sank),
                Count = length(dst_sank))%>%
  glimpse()


# Make Null datasets----
# Group1
N = data.frame(dst_sank=seq(0,2403.4, length=3568),
                zone="N",
                Model="NULL")

S = data.frame(dst_sank=seq(0,2264.77, length=970),
                   zone="S",
                Model="NULL")

W = data.frame(dst_sank=seq(0,1637.92, length=195),
                      zone="W",
                Model="NULL")


```




# Combine observed and null datasets for other data
this will create NA for lat,long,year
```{r}

dat.model<- dat.pots%>%
  bind_rows(N,S,W)%>%
  glimpse()

```



# View Null models
Take note that this Null model assumes we have equal probrabilty of finding lobster (and pots) with increasing distance from the sanctuaries




## Plot the observed and null
```{r}

ggplot(dat.model, aes(x=dst_sank))+
  geom_density(alpha=.5)+
  #   geom_histogram(aes(y=..density..))+
  #   facet_wrap( ~ Nearest.Sanctuary,scales = "free",ncol = 2)
  facet_grid( Model~ zone,scales = "free")


```




Save the data
```{r}

setwd(data.dir)

write_csv(dat.model,"dat.model.csv")

```










[Analysis-lobster-pots](https://github.com/UWA-BIOL4408-Marine-Ecology/Analysis-lobster-pots/blob/master/README.md)


[3_lobster-pot-test](https://github.com/UWA-BIOL4408-Marine-Ecology/Analysis-lobster-pots/blob/master/3_lobster-pot-test.md)
