---
title: "BIOL4408 Marine Ecology: lobster pots 1."
author: "TimLanglois"
date: "09/01/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# 2. Create Null lobster pot data


Need to install a missing library
```{r}
# install.packages("sm")

```



Load some librarys
```{r libs1, message=FALSE, warning=FALSE}
library(tidyr)
library(plyr)
library(dplyr)
library(ggplot2)
library(readr) #to write data
library(here) #to make robust links to files
# And you will need these libraries
library(ggmap)
library(argosfilter)
library(sm)
library(KernSmooth)

```


Write a function that will be useful later on - a general search and replace function
```{r}
gsr <- function(Source, Search, Replace) { 
  if (length(Search) != length(Replace))     stop("Search and Replace Must Have Equal Number of Items\n") 
  Changed <- as.character(Source)
  for (i in 1:length(Search)) 
  { 
    cat("Replacing: ", Search[i], " With: ", Replace[i], "\n")
    Changed <- replace(Changed, Changed == Search[i], Replace[i])   } 
  cat("\n")   
  Changed 
}
```





It is useful to set a study name
```{r name, message=FALSE, warning=FALSE}
study<-"lobster.pots"
```



We are going to use the here() function, which creates a shortcut to your location.


Check what the here() function returns in your environment? and adapt to suit

Again - we have to use here::here() - due to conflict with plyr::here()
```{r , message=FALSE, warning=FALSE}
here::here()
```

If you are using an ecocloud server - you will probrably have to add folder names to the here() function 

#here::here("workspace","Template-lobster-pots","Data")

Let's make a shortcut to that "Data" directory.
```{r here, message=FALSE, warning=FALSE}

data.dir <- here::here("Data")

#or for ecocloud

#data.dir <- here::here("workspace","Template-lobster-pots","Data")
```


Let's make a plots directory and then shortcut to that directory.
```{r here, message=FALSE, warning=FALSE}

dir.create(file.path(here::here(), "Plots")) #create Data folder

plot.dir <- here::here("Plots")

#or for ecocloud
#dir.create(file.path(here(), "workspace","Template-lobster-pots","Plots")) #create Data folder

#data.dir <- here("workspace","Template-lobster-pots","Plots")
```



Read in pot data
```{r warning=FALSE}
setwd(data.dir)
dat<-read_csv("lobster.pots.2019-01-23.csv")%>%
  glimpse()

```


bring in more lobster pot data
```{r}
setwd(data.dir)

lob.pot1<-read_csv("2018_Group1.csv")%>%
  glimpse()


lob.pot2<-read_csv("2018_Group2.csv")%>%
  glimpse()





```



# Divide data between sanctuary locations----

```{r}
# Group 1 
parker1<-lob.pot1[lob.pot1$X>115.51&lob.pot1$Y<(-32.015),]
green1<-lob.pot1[lob.pot1$X<115.51&lob.pot1$Y<(-32.015)&lob.pot1$X>115.47,]
armstrong1<-lob.pot1[lob.pot1$Y>(-32.005),]

parker1=data.frame(parker1,"location"=c("parker"))
green1=data.frame(green1,"location"=c("green"))
armstrong1=data.frame(armstrong1,"location"=c("armstrong"))

# Group 2
parker2<-lob.pot2[lob.pot2$X>115.51&lob.pot2$Y<(-32.015),]
green2<-lob.pot2[lob.pot2$X<115.51&lob.pot2$Y<(-32.015)&lob.pot2$X>115.47,]
armstrong2<-lob.pot2[lob.pot2$Y>(-32.005),]


parker2=data.frame(parker2,"location"=c("parker"))
green2=data.frame(green2,"location"=c("green"))
armstrong2=data.frame(armstrong2,"location"=c("armstrong"))


lob.pot1.all<-rbind(parker1,green1,armstrong1)
lob.pot2.all<-rbind(parker2,green2,armstrong2)

```




Insert the centre of each sanctuary
```{r}

lob.pot1.all$Sanctuary.centre.Lat<-lob.pot1.all$location
lob.pot2.all$Sanctuary.centre.Lat<-lob.pot2.all$location

lob.pot1.all$Sanctuary.centre.Long<-lob.pot1.all$location
lob.pot2.all$Sanctuary.centre.Long<-lob.pot2.all$location


Sanctuary.names<-c("armstrong","parker","green")
Sanctuary.centre.Lat<-c("-31.98931","-32.02517","-32.02225")
Sanctuary.centre.Long<-c("115.5086","115.5243","115.49755")


```


# Match up the lat and long
```{r}

lob.pot1.all$Sanctuary.centre.Long <- gsr(lob.pot1.all$Sanctuary.centre.Long, Sanctuary.names, Sanctuary.centre.Long)
lob.pot1.all$Sanctuary.centre.Lat <- gsr(lob.pot1.all$Sanctuary.centre.Lat, Sanctuary.names, Sanctuary.centre.Lat)
head(lob.pot1.all)


lob.pot2.all$Sanctuary.centre.Long <- gsr(lob.pot2.all$Sanctuary.centre.Long, Sanctuary.names, Sanctuary.centre.Long)
lob.pot2.all$Sanctuary.centre.Lat <- gsr(lob.pot2.all$Sanctuary.centre.Lat, Sanctuary.names, Sanctuary.centre.Lat)
head(lob.pot2.all)

lob.pot1.all$Sanctuary.centre.Lat<-(as.numeric(lob.pot1.all$Sanctuary.centre.Lat))
lob.pot1.all$Sanctuary.centre.Long<-(as.numeric(lob.pot1.all$Sanctuary.centre.Long))

lob.pot2.all$Sanctuary.centre.Lat<-(as.numeric(lob.pot2.all$Sanctuary.centre.Lat))
lob.pot2.all$Sanctuary.centre.Long<-(as.numeric(lob.pot2.all$Sanctuary.centre.Long))
```


Use argosfilter() to find the distance by great circle route/curvature of the earth
```{r warning=FALSE}
# distance-Function distance calculates the distance, in km, between two geographical locations following the great circle route

lob.pot1.all$distance<-distance(lat1=lob.pot1.all$Sanctuary.centre.Lat,lat2=lob.pot1.all$Y,lon1=lob.pot1.all$Sanctuary.centre.Long,lon2=lob.pot1.all$X)%>%
  glimpse()


lob.pot2.all$distance<-distance(lat1=lob.pot2.all$Sanctuary.centre.Lat,lat2=lob.pot2.all$Y,lon1=lob.pot2.all$Sanctuary.centre.Long,lon2=lob.pot2.all$X)%>%
  glimpse()

```


# Create Null model for tests
```{r}
summary1<-plyr::ddply(lob.pot1.all,.(location), summarise,
                Max = max(distance),
                Min = min(distance),
                Count = length(distance))%>%
  glimpse()


# Make Null datasets----
# Group1
armstrong1.m = data.frame(distance=seq(0.6655149,4.964157, length=354),
                location="armstrong",
                Model="NULL")

green1.m = data.frame(distance=seq(0.3669323,2.416857, length=106),
                   location="green",
                Model="NULL")

parker1.m = data.frame(distance=seq(0.4999049,3.081829, length=168),
                      location="parker",
                Model="NULL")



summary2<-ddply(lob.pot2.all,.(location), summarise,
                Max = max(distance),
                Min = min(distance),
                Count = length(distance))%>%
  glimpse()

# Group2
armstrong2.m = data.frame(distance=seq(0.5877408,4.380596, length=394),
                          location="armstrong",
                          Model="NULL")

green2.m = data.frame(distance=seq(0.5249063,2.522132, length=36),
                      location="green",
                      Model="NULL")

parker2.m = data.frame(distance=seq(0.5155369,2.955497, length=84),
                       location="parker",
                       Model="NULL")


lob.pot1.all$Model<-"Pots"

lob.pot2.all$Model<-"Pots"

keep<-c("distance","location","Model")
lob.pot1.a<-lob.pot1.all[keep]
lob.pot2.a<-lob.pot2.all[keep]
```

glimpse(dat)




# Create Null using other data model for tests
```{r}

dat.pots<-dat%>%
  dplyr::select(dst_sank,zone,lat,lon,year)%>%
  mutate(Model="Pots")%>%
  glimpse()

summary1<-plyr::ddply(dat,.(zone), summarise,
                Max = max(dst_sank),
                Min = min(dst_sank),
                Count = length(dst_sank))%>%
  glimpse()


# Make Null datasets----
# Group1
N = data.frame(dst_sank=seq(0,2403.4, length=3568),
                zone="N",
                Model="NULL")

S = data.frame(dst_sank=seq(0,2264.77, length=970),
                   zone="S",
                Model="NULL")

W = data.frame(dst_sank=seq(0,1637.92, length=195),
                      zone="W",
                Model="NULL")


```





# Combine observed and null datasets
```{r}
lob.pot1.all.null<-rbind(lob.pot1.a,armstrong1.m,green1.m,parker1.m)

lob.pot2.all.null<-rbind(lob.pot2.a,armstrong2.m,green2.m,parker2.m)
```



# Combine observed and null datasets for other data
this will create NA for lat,long,year
```{r}

dat.model<- dat.pots%>%
  bind_rows(N,S,W)%>%
  glimpse()

```



# View Null models
Take note that this Null model assumes we have equal probrabilty of finding lobster (and pots) with increasing distance from the sanctuaries


## Group 1
```{r}

Pots1<-ggplot(lob.pot1.all.null, aes(x=distance))+
  geom_density(alpha=.5)+
  ggtitle("Group 1")+
  #   geom_histogram(aes(y=..density..))+
  #   facet_wrap( ~ Nearest.Sanctuary,scales = "free",ncol = 2)
  facet_grid( Model~ location,scales = "free")

Pots1
```


## Group 2

```{r}
Pots2<-ggplot(lob.pot2.all.null, aes(x=distance))+
  geom_density(alpha=.5)+
  ggtitle("Group 2")+
  #   geom_histogram(aes(y=..density..))+
  #   facet_wrap( ~ Nearest.Sanctuary,scales = "free",ncol = 2)
  facet_grid( Model~ location,scales = "free")

Pots2
```




## Plot the observed and null
```{r}

ggplot(dat.model, aes(x=dst_sank))+
  geom_density(alpha=.5)+
  #   geom_histogram(aes(y=..density..))+
  #   facet_wrap( ~ Nearest.Sanctuary,scales = "free",ncol = 2)
  facet_grid( Model~ zone,scales = "free")


```




Save the data
```{r}

setwd(data.dir)

write_csv(dat.model,"dat.model.csv")

```




















Go back to [Analysis-lobster-pots](https://github.com/UWA-BIOL4408-Marine-Ecology/Analysis-lobster-pots/blob/master/README.md)

Go forward to [2_lobster-pot-model](https://github.com/UWA-BIOL4408-Marine-Ecology/Analysis-lobster-density/blob/master/2_lobster-density_check-data.md)