---
title: "BIOL4408 Marine Ecology: lobster pots 1."
author: "TimLanglois"
date: "09/01/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# 3. Test lobster pot data

1. Test null against observed


Need to install a missing library
```{r}
# install.packages("sm")

```


Load some librarys
```{r libs1, message=FALSE, warning=FALSE}
library(tidyr)
library(plyr)
library(dplyr)
library(ggplot2)
library(readr) #to write data
library(here) #to make robust links to files
# And you will need these libraries
library(ggmap)
library(sm)
library(KernSmooth)

```


Source function
# See Langlois et al. 2012 PLoS ONE for details and information on the method
# To test for each Sanctuary by changing the subset
```{r}
source("1_Load function KDE.R")
```


It is useful to set a study name
```{r name, message=FALSE, warning=FALSE}
study<-"lobster.pots"
```


Again - we have to use here::here() - due to conflict with plyr::here()
```{r , message=FALSE, warning=FALSE}
here::here()
```

If you are using an ecocloud server - you will probrably have to add folder names to the here() function 

#here::here("workspace","Template-lobster-pots","Data")

Let's make a shortcut to that "Data" directory.
```{r here, message=FALSE, warning=FALSE}

data.dir <- here::here("Data")

#or for ecocloud

#data.dir <- here::here("workspace","Template-lobster-pots","Data")
```


Let's make a plots directory and then shortcut to that directory.
```{r , message=FALSE, warning=FALSE}

dir.create(file.path(here::here(), "Plots")) #create Data folder

plot.dir <- here::here("Plots")

#or for ecocloud
#dir.create(file.path(here(), "workspace","Template-lobster-pots","Plots")) #create Data folder

#data.dir <- here("workspace","Template-lobster-pots","Plots")
```



Read in pot model data and rename to match fields required by function
```{r warning=FALSE}
setwd(data.dir)
dat.model<-read_csv("dat.model.csv")%>%
   dplyr::select("dst_sank","zone","Model")%>%
  dplyr::rename(distance = dst_sank,
                location = zone)%>%
  glimpse()


```


Run the KDE tests
# KDE test----
#Test of distribution - this will generate a P value and a plot
# See Langlois et al. 2012 PLoS ONE for details and information on the method
# To test for each zone by changing the subset

North
```{r message=TRUE, paged.print=TRUE}

WF(filter(dat.model,location=="N"),50,'Model')

```


South
```{r}

WF(filter(dat.model,location=="S"),50,'Model')

```


West
```{r}

WF(filter(dat.model,location=="W"),50,'Model')

```







[Analysis-lobster-pots](https://github.com/UWA-BIOL4408-Marine-Ecology/Analysis-lobster-pots/blob/master/README.md)



